### 2019-02-27 paper/ms.tex
Setup pre-Fisher matrix formalism

>>>>

One could proceed as we did previously \citep{2018arXiv181110609B}, estimating
the auto-spectra in each line by forming suitable products and ratios of the
various cross-spectra. However, we instead take a slightly different approach
here by performing a joint fit for all of the various auto-spectra. First, we
assume a measurement of each of $\xps{i}{j}$. Then the relevant variance and
covariances are \citep[e.g.][]{2015JCAP...03..034V},
\beq
\begin{split}
\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} + \xps{i}{j}\xps{i}{k}\text{.}
\end{split}
\eeq
We are then making a measurement of each of $\xps{i}{j}$, $\xps{j}{k}$,
and $\xps{k}{i}$. We further model each of these power spectra as,
\beq
\xps{i}{j}(k) = B_i(k) B_j(k) \denps(k)\text{.}
\eeq
That is, we are only working in the regime where $r_{i,j}=1$. What this
translates to is that we may only perform this interloper removal on
sufficiently large scales, i.e. where $k<k_{\text{max}}$, where
$k_{\text{max}}$ is set by wherever the lines $i$ and $j$ start to
decorrelate. The value of $k_{\text{max}}$ is the only aspect of our analysis
that is model dependent.
